Software Ticket Quality

### 2017-10-16 proposal/mprop.tex
Completed the contextual polarity paper summary

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to experiment with automatically distinguishing
    between contextual and prior polarity.
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

>>>>

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to find efficient ways to distinguish between 
    contextual and prior polarity.
  \item \textbf{What was the method?}
    They used a two step method that used machine learning and a variety of
    features. The first step classified each phrase which had a clue as either
    neutral or polar, followed by taking all phrases marked in the previous step
    and giving them a contextual polarity (e.g.\ positive, negative, both, neutral).
  \item \textbf{What did they learn?}
    Through the method the authors employed, they managed to automatically identify
    the contextual polarity. As most papers were only looking at the sentiment  
    extracted from the overall document, they managed to get valuable results
    from looking at specific words and phrases.
  \item \textbf{Relevance to our work}: when analyzing the description and
    comments of the ticket, we can use their method for accurately 
    infering the sentiment transmitted.
\end{itemize}
